GiftGiver: The Gift Recommender \\ {\small AAI -- Instructor: Prof. Jane Hsu}

### 2011-06-23 paper/paper.tex
modify some syntax error

\subsection{Flow}
Users of our recommender system starts with filling in their considerations on the UI interface. (For reducing the loading of senders, we using check box and combo box and make a lot of common option.)   
After filling in the options and considerations, the users will be greeted  a list of 20 recommended gifts generated by the system from the information provided by the users.
If the users want more information on the recommended gift item, they can click the link and the system will help the users to find the relative products from several popular e-commerce websites.

@@

Furthermore, we interviewed 5 differnet people the primary concerns when picking a nice gift. We later found out the result of the interviews that they agreeed the same considerations with the questionnaire results. The results had shown that people  concern about the occasion more than relationship.  Other considerations did not seem to influence too much to the decision making process compared to occasion and relationship.

@@

Compare to major e-commerce websites that sells real products, our website doesn't have the real database for all different kinds of gifts, but we had a better flow and more variety and flexibility of options for users to pick. There is also another extinction between our UI design and those of major corporations. For example, Gifts.com has 9 ages degree, such as 0~6, 7~12, 13~19, 20~30, 31~40 etc, we use fuzzy set to define our age instead of clear separation by years. Because nouns like child, adult etc. will help the system in the commonsense part.  On the other hand, some people still looks like a child even that person has already more than 30s.  The fuzzy part will come out positive result.

@@

This section briefly discussed our appoaches to ranking the gifts and algorithms with commonsense knowledge base

@@

\subsubsection{Commonsense knowledge base}
In our system, we use Open Mind Common Sense, a knowledge corpus that contains 800,000 sentences about everyday life, gathered from Web volunteers. Using this resource, we successfully built a fashion recommendation system.

>>>>

\subsection{Flow}
Users of our recommender system start with filling in their considerations on the UI interface. (For reducing the loading of senders, we use check box and combo box and make a lot of common options.)   
After filling in the options and considerations, the users will be greeted  a list of 20 recommended gifts generated by the system from the information provided by the users.
If the users want more information on the recommended gift item, they can click the link and the system will help the users to find the relative products from several popular e-commerce websites.

@@

Furthermore, we interviewed 5 differnet people with the primary concerns when picking a nice gift. We later found out the result of the interviews that they agreeed the same considerations with the questionnaire results. The results had shown that people  concern about the occasion more than relationship.  Other considerations did not seem to influence too much to the decision making process compared to occasion and relationship.

@@

Compare to major e-commerce websites that sells real products, our website doesn't have the real database for all different kinds of gifts, but we had a better flow and more variety and flexibility of options for users to pick. There is also another extinction between our UI design and those of major corporations. For example, Gifts.com has 9 ages degree, such as [0-6], [7-12], [13-19], [20-30], [31-40] etc, we use fuzzy set to define our age instead of clear separation by years. Because nouns like child, adult etc. will help the system in the commonsense part.  On the other hand, some people still looks like a child even that person has already more than 30s.  The fuzzy part will come out positive result.

@@

This section briefly discussed our appoaches to rank the gifts and algorithms with commonsense knowledge base

@@

\subsubsection{Commonsense knowledge base}
In our system, we use Open Mind Common Sense, a knowledge corpus that contains 800,000 sentences about everyday life, gathered from Web volunteers. Using this resource, we successfully built a fashion recommender system.
